Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-08-15 alloscore_manuscript/manuscript.Rnw
wording cleanup
Update alloscore_manuscript/manuscript.Rnw

Thirdly, we emphasize that we opted at this stage of
development to explicitly rule out situations where a successful
epidemiological forecast could lead to policy decisions that change the distribution of the predicted outcome $Y$. 
For example, this excludes the important problem of allocation of doses of a preventative vaccine.
We have not developed a formal approach to forecast evaluation using scores given by \eqref{eqn:AS-orc} when both
disease burden and unmet need are considered as endogenous variables. Our sense is that such an approach would require some form of
accounting for the causal effect of the allocation decision on observed measures of disease burden, e.g. estimating the (counterfactual)
cases or deaths averted from one or another allocation strategy through the available observed data.

>>>>

Thirdly, we emphasize that we opted at this stage of
development to explicitly rule out situations where a successful
epidemiological forecast could lead to policy decisions that change the distribution of the predicted outcome $Y$. 
For example, this excludes the important problem of allocation of doses of a preventative vaccine.
We have not developed a formal approach to forecast evaluation using scores given by \eqref{eqn:AS-orc} when both
disease burden and unmet need are considered as endogenous variables. Such an approach would require some form of
accounting for the causal effect of the allocation decision on observed measures of disease burden, e.g. using the available observed data to estimate the (counterfactual)
number of cases or deaths averted from one or another allocation strategy.
